Manifold Destiny - or how to rig an election

### 2024-01-01 index.qmd
paperadd

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
```

### Simulation
```{webr-r}
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
SimVoterdatabase(app_bal)
app_n_rep <- selreport(app0,md$app0)
app_n_out <- seloutput(app_n_rep)
```

### Applications
```{webr-r}
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
app0_rp <- selreport(app0,md$app0)
app_0_out <- seloutput(app0_rp)
app1_rp <- selreport(app1,md$app1)
app_1_out <- seloutput(app1_rp)
app2_rp <- selreport(app2,md$app2)
app_2_out <- seloutput(app2_rp)
app3_rp <- selreport(app2,md$app2)
app_3_out <- seloutput(app2_rp)
app4_rp <- selreport(app2,md$app2)
app_4_out <- seloutput(app2_rp)
```

>>>>

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(combinat)
```

### Simulation
```{webr-r}
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
SimVoterdatabase(app_bal)
app_n_rep <- selreport(app_bal,md$app0)
app_n_out <- seloutput(app_n_rep)
app_n_sim <- SimVoterdatabase(app_bal)
```

### Applications

#### App1
```{webr-r}
app1_rp <- selreport(app1,md$app1)
app_1_out <- seloutput(app1_rp)
```

#### App2
```{webr-r}
app2_rp <- selreport(app2,md$app2)
app_2_out <- seloutput(app2_rp)
```

### 2024-01-01 presentation.qmd

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@

---

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
print(SimVoterdatabase(app_bal))
```

>>>>

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
#webr: 
#  show-startup-message: true    # Disable displaying status of webR initialization
#  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
##filters:
#- webr 
#footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

@@
